Initial estuarine response to the nutrient dense Piney Point wastewater discharge into Tampa Bay, Florida

### 2021-10-14 manu-draft.Rmd
reprocess all tables up to Oct, need to update manu text

maxdt <- as.Date('2021-08-01')

@@

From April through July 2021, `r nwq` samples were collected for chl-a, dissolved oxygen, total nitrogen, total phosphorus, total ammonia nitrogen, nitrate/nitrite, pH, salinity, secchi depth, and temperature (Table \@ref(tab:wqsumtab)).  Of these samples, `r outrng`\% were outside of the normal range defined by the long-term monthly monitoring data for the baseline period from 2006 to 2020 (below for Secchi depth, above for all others). The percentage of observations outside of the normal range varied by location and parameter.  For chl-a, `r chlabv[['1']]`\% of the observations were above the normal range for area 1, whereas only `r chlabv[[2]]`\% and `r chlabv[[3]]`\% were above for areas 2 and 3, respectively. Total nitrogen concentrations were above the normal range for `r tnabv[['1']]`\% of observations in area 1, whereas concentrations were above for `r tnabv[['2']]`\% of observations in area 2 and `r tnabv[['3']]`\% in area 3.  Secchi observations were below the normal range for `r secblw[['1']]`\% of observations in area 1 and for `r secblw[['2']]`\% and `r secblw[['3']]`\% of observations in areas 2 and 3.  Notable differences were also observed for dissolved oxygen (e.g., `r dosabv[['1']]`\% were above in area 1, `r dosabv[['2']]`\% in area 2).  Physical parameters (salinity, temperature) were generally within range over the study period. Inorganic nitrogen (ammonia, nitrate/nitrite) was generally within range, although initial time series showed much higher concentrations for ammonia in April near area 1, similar to the effluent measurements in Table \@ref(tab:stktab). Spatial variation among the parameters showed that values were generally above the normal range (or below for Secchi depth) for many locations near Piney Point, Anna Maria Sound, and the northern mouth of Tampa Bay (Figure \@ref(fig:wqmap)).

>>>>

maxdt <- as.Date('2021-10-01')

@@

From April through September 2021, `r nwq` samples were collected for chl-a, dissolved oxygen, total nitrogen, total phosphorus, total ammonia nitrogen, nitrate/nitrite, pH, salinity, secchi depth, and temperature (Table \@ref(tab:wqsumtab)).  Of these samples, `r outrng`\% were outside of the normal range defined by the long-term monthly monitoring data for the baseline period from 2006 to 2020 (below for Secchi depth, above for all others). The percentage of observations outside of the normal range varied by location and parameter.  For chl-a, `r chlabv[['1']]`\% of the observations were above the normal range for area 1, whereas only `r chlabv[[2]]`\% and `r chlabv[[3]]`\% were above for areas 2 and 3, respectively. Total nitrogen concentrations were above the normal range for `r tnabv[['1']]`\% of observations in area 1, whereas concentrations were above for `r tnabv[['2']]`\% of observations in area 2 and `r tnabv[['3']]`\% in area 3.  Secchi observations were below the normal range for `r secblw[['1']]`\% of observations in area 1 and for `r secblw[['2']]`\% and `r secblw[['3']]`\% of observations in areas 2 and 3.  Notable differences were also observed for dissolved oxygen (e.g., `r dosabv[['1']]`\% were above in area 1, `r dosabv[['2']]`\% in area 2).  Physical parameters (salinity, temperature) were generally within range over the study period. Inorganic nitrogen (ammonia, nitrate/nitrite) was generally within range, although initial time series showed much higher concentrations for ammonia in April near area 1, similar to the effluent measurements in Table \@ref(tab:stktab). Spatial variation among the parameters showed that values were generally above the normal range (or below for Secchi depth) for many locations near Piney Point, Anna Maria Sound, and the northern mouth of Tampa Bay (Figure \@ref(fig:wqmap)).
